---
title: "British Social Attitudes - Population Segmentation"
author: "Francisco Marco-Serrano"
date: "08 October 2015"
output: html_document
---

Attitudinal population segmentation is a research project into the British society regarding attitudes to several societal topics, including Higher Education, with the aim of segmenting population beyond the typical income-based measures and relationship or sociological perspectives.

#Data

Data is from the British Social Attitudes Survey 2013, obtained from the UK Data Service.

> NatCen Social Research, British Social Attitudes Survey, 2013 [computer file]. Colchester, Essex: UK Data Archive [distributor], July 2014. SN: 7500, http://dx.doi.org/10.5255/UKDA-SN-7500-1


```{r}
library(caret)

setwd("~/British Social Attitudes 2013")
bas13 <- read.delim("bsa13ukds.tab", header = TRUE, sep = "\t")

#Housekeeping for machine learning
# keep only cat 1 to 4
bas13 <- bas13[ which(bas13$Himp>0 & bas13$Himp<5), ]
bas13$Himp <- as.factor(bas13$Himp)


set.seed(123)
inTraining <- createDataPartition(bas13$Serial, p = .75, list = FALSE)

#variables to exclude
#todo: exclude variable to be used to imputate
exclude <- c(1:99)

bas13.train <- bas13[inTraining, -exclude]
bas13.test <- bas13[-inTraining, -exclude]

```

Questionnaire can be found at http://doc.ukdataservice.ac.uk/doc/7500/mrdoc/pdf/bsa2013_capi_final_questionnaire.pdf

Metadata can be found at http://nesstar.esds.ac.uk/webview/


#Analysis

Variable to explain is 'Himp': How important it is for a young person to go on to a university or college?

```{r, echo=FALSE}
library(randomForest)

set.seed(123)
fitControl <- trainControl(## 10-fold CV
                           method = "repeatedcv",
                           number = 10,
                           ## repeated ten times
                           repeats = 10)

fit.rf <- train(Himp~., data=bas13.train,
                method="rf", trcontrol=fitControl, verbose=FALSE)

fit.rf
save(fit.rf, file = "rf.RData")

fit.rf$finalModel

plot(fit.rf)

# Show Top 20 variables in importance
varImp(fit.rf, scale=FALSE)


# And the out-of-sample accuracy
predict.rf <- predict(fit.rf, newdata=bas13.test)
confusionMatrix(data = predict.rf, bas13.test$Himp)

```

The main characteristics determining the answer to question Q379 are (ordered in descending importance):

* UniFibet - University attender will end up better off financially
* EdSpnd1c - Highest priority for extra government spending on education?
* UniDebts - University cost leads to debt he/she can't afford to repay
* ChLikUn2 - How likely that any of your children who are still at school will go to university?
* PTPay - Who should pay the largest share of tuition fees for those studying part-time
* Statsec2 - State secondary schools nowadays teach young people basic skills such as reading, writing and maths
* PrimImp2 - Second most useful one for improving the education of children in primary schools
* PTFee - Which part time students should get financial support from government?
* InStuCu - International students from outside the EU bring with them significant cultural benefits to Britain.
* NHSPri1 - Most important area of NHS work.


For imputation purposes, questions Q809-841 & 880-895 (National Identity), Q849 (life satisfaction), 896-897 (disability), 899-973 (education), 1041-1051 (income).
