---
title: "British Social Attitudes - Population Segmentation"
author: "Francisco Marco-Serrano"
date: "08 October 2015"
output: pdf_document
---

Attitudinal population segmentation is a research project into the British society regarding attitudes to several societal topics, including Higher Education, with the aim of segmenting population beyond the typical income-based measures and relationship or sociological perspectives.

#Data

Data is from the British Social Attitudes Survey 2013, obtained from the UK Data Service.

> NatCen Social Research, British Social Attitudes Survey, 2013 [computer file]. Colchester, Essex: UK Data Archive [distributor], July 2014. SN: 7500, http://dx.doi.org/10.5255/UKDA-SN-7500-1


```{r}
library(caret)

setwd("~/British Social Attitudes 2013")
bas13 <- read.delim("bsa13ukds.tab", header = TRUE, sep = "\t")

#Housekeeping for machine learning
bas13$Himp <- as.factor(bas13$Himp)


set.seed(123)
inTraining <- createDataPartition(bas13$Serial, p = .7, list = FALSE)
bas13.train <- bas13[inTraining, -c(1:3)]
bas13.test <- bas13[-inTraining, -c(1:3)]

```

Questionnaire can be found at http://doc.ukdataservice.ac.uk/doc/7500/mrdoc/pdf/bsa2013_capi_final_questionnaire.pdf

Questions about Higher Education are:

Q375. HEFee - I'm now going to ask you what you think about university or college
students or their families paying towards the costs of their
tuition, either while they are studying or after they have
finished. Which of the views on this card comes closest to what
you think about that?

Q376. FeesUni - Which of the following statements comes closest to your own view?

Q377. FeesSub - And which of these two statements comes closest to your own view?

Q378. HEGrant2 - And, at present, some full-time British university students get
grants to help cover their living costs. Getting a grant depends
upon the student's circumstances and those of their family. Do you
think that...?

Q379. Himp - And how important do you think it is for a young person to go on to
higher education - to a university or college?

Q380. HEFtPt - In general, do you think that young people studying for higher education qualifications at universities and colleges should study full-time for three or four years or do you think they should study part-time while working, taking longer to complete their courses?

```{r, echo=FALSE}
library(randomForest)

set.seed(123)
fitControl <- trainControl(## 10-fold CV
                           method = "repeatedcv",
                           number = 10,
                           ## repeated ten times
                           repeats = 10)

fit.rf <- train(Himp~., data=bas13.train,
                method="rf", trcontrol=fitControl, verbose=FALSE)

fit.rf
save(fit.rf, file = "rf.RData")

fit.rf$finalModel

plot(fit.rf)

# Show Top 20 variables in importance
varImp(fit.rf, scale=FALSE)


# And the out-of-sample accuracy
predict.rf <- predict(fit.rf, newdata=bas13.test)
confusionMatrix(data = predict.rf, bas13.test$Himp)

```

The main characteristics determining the answer to question Q379 are (ordered in descending importance):

*UniFibet - University attender will end up better off financially

*EdSpnd1c - Highest priority for extra government spending on education?

*UniDebts - University cost leads to debt he/she can't afford to repay

*ChLikUn2 - How likely that any of your children who are still at school will go to university?

*PTPay - Who should pay the largest share of tuition fees for those studying part-time

*Statsec2 - State secondary schools nowadays teach young people basic skills such as reading, writing and maths

*PrimImp2 - Second most useful one for improving the education of children in primary schools

*PTFee - Which part time students should get financial support from government?

*InStuCu - International students from outside the EU bring with them significant cultural benefits to Britain.

*NHSPri1 - Most important area of NHS work.
